\change{The effect of the COVID-19 pandemic on arXiv pre-prints in maths, physics, computer science, and quantitative biology}

### 2022-10-31 article/ms.tex
last ref

The COVID-19 pandemic appears to have had minimal impact on collective research productivity \change{in the science and technology specialisations we examined}, \change{and that is before accounting for the tremendous work in scientific communication and contributions to public policy throughout the pandemic.} \change{These findings are at odds with similar studies in fields that have larger research overlap with the SARS-CoV-2 virus. For example, publications in life sciences saw a 6.5 fold increase in subject headings related to COVID-19\cite{Riccaboni}. The effects of the pandemic clearly impact research specialisations differently, and we note some significant changes within specific research areas. The largest persistent decline in pre-prints has occurred in general physics (arXiv primary category \texttt{physics}), largely due to a decline in  pre-prints posted to computational and applied physics areas within the \texttt{physics} primary category. As of mid-2022, this steady decline continues. Amongst individual fields the largest \emph{relative} decline in a single field is explainable by a high energy lattice physics conference that was cancelled in 2020.}

@@

>>>>

The COVID-19 pandemic appears to have had minimal impact on collective research productivity \change{in the science and technology specialisations we examined}, \change{and that is before accounting for the tremendous work in scientific communication and contributions to public policy throughout the pandemic.} \change{These findings are at odds with similar studies in fields that have larger research overlap with the SARS-CoV-2 virus\cite{Fraser}. For example, publications in life sciences saw a 6.5 fold increase in subject headings related to COVID-19\cite{Riccaboni}. The effects of the pandemic clearly impact research specialisations differently, and we note some significant changes within specific research areas. The largest persistent decline in pre-prints has occurred in general physics (arXiv primary category \texttt{physics}), largely due to a decline in  pre-prints posted to computational and applied physics areas within the \texttt{physics} primary category. As of mid-2022, this steady decline continues. Amongst individual fields the largest \emph{relative} decline in a single field is explainable by a high energy lattice physics conference that was cancelled in 2020.}

@@

\bibitem{Fraser}
Fraser N, Brierley L, Dey G, Polka JK, Pálfy M, Nanni F, et al., {The evolving role of preprints in the dissemination of COVID-19 research and their impact on the science communication landscape}, \emph{PLOS Biology}, \textbf{19}, 4, doi:10.1371/journal.pbio.3000959 \newblock (2021).
